An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-05-03 CMPSpaper_writing/CMPSpaper_writing.Rmd
tiles plot

```{r, echo=FALSE}
dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_score)) + 
  geom_tile() + 
  geom_tile(aes(colour="same barrel"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
  scale_colour_manual("Source", values="darkorange") +
  facet_grid(bulletA ~ bulletB, labeller = "label_both") + xlab("Land B") + 
  ylab("Land A") + theme(aspect.ratio = 1) +
  geom_text(aes(label=cmps_score)) +
  theme_bw() +
  theme(aspect.ratio = 1)
```

>>>>

```{r tiles, echo=FALSE, fig.cap="Overview of all 36 CMPS scores resulting from a bullet-to-bullet comparison of all six lands on each bullet.", out.width=".7\\textwidth", fig.align="center"}
dframe <- dframe %>% mutate(
  landA = paste0("L", landA),
  landB = paste0("L", landB),
  landB = factor(landB, levels = paste0("L", c(2:6,1))),
  bulletA = paste0("Bullet ", bulletA),
  bulletB = paste0("Bullet ", bulletB)
)

dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) + 
  geom_tile() + 
  geom_tile(aes(colour="same barrel"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
  scale_colour_manual("Source", values="darkorange") +
  facet_grid(bulletB ~ bulletA) + xlab("Land A") + 
  ylab("Land B") + theme(aspect.ratio = 1) +
  geom_text(aes(label=cmps_score)) +
  theme_bw() +
  theme(aspect.ratio = 1)
```
